Tree regeneration in models of forest dynamics: a key priority for further research

### 2023-05-15 manuscript/manuscriptRW.Rmd
add all authors affiliations in the date section and allignt

---
title: "Tree regeneration in models of forest dynamics: a key priority for further research"
author:
- Olalla Díaz-Yáñez,
- Yannek Käber,
- Tim Anders,
- Friedrich Bohn,
- Kristin H. Braziunas,
- Josef	Brůna,
- Rico Fischer,
- Samuel M. Fischer,
- Jessica Hetzer,
- Thomas Hickler,
- Christian	Hochauer,
- Manfred J. Lexer,
- Heike	Lischke,
- Mats Mahnken,
- Paola	Mairota,
- Ján Merganič,
- Katarina Merganičová,
- Tobias Mette,
- Marco Mina,
- Xavier Morin,
- Werner Rammer,
- Christopher P.O. Reyer,
- Simon	Scheiter,
- Daniel Scherrer,
- Harald Bugmann
date: "`r Sys.Date()`"
output:
  bookdown::pdf_document2:
    keep_tex: yes
    number_sections: yes
    toc: no
    extra_dependencies: "subfig"
  word_document:
    reference_docx: template_paper.docx
mainfont: Arial
fontsize: 12pt
linestretch: 1.5
bibliography: Regeneration.bib
link-citations: yes
nocite: |
  @bugmann1996a, @bohn2014, @fabrika2005, @mette2014, @smith2001a, @langan2017, @seidl2012a, @lischke2006, @schumacher2006, @scheiter2009, @scheller2007, @morin2021, @lasch-born2020, @hickler2012, @fischer_lessons_2016, @langan2017, @scheiter2013 
linkcolor: blue
csl: global-change-biology.csl
editor_options:
  markdown:
    wrap: 72
header-includes:
- \usepackage[left]{lineno}
- \linenumbers
- \usepackage{caption}
- \captionsetup[figure]{font=scriptsize}
- \captionsetup[table]{font=scriptsize}
---

>>>>

---
pretitle: "Journal: Ecological Monographs. Manuscript type: Article"
title: "Tree regeneration in models of forest dynamics: a key priority for further research"
author: 
- Olalla Díaz-Yáñez$^{*1}$, 
- Yannek Käber$^1$, 
- Tim Anders$^2$,
- Friedrich Bohn$^3$,
- Kristin H. Braziunas$^4$,
- Josef	Brůna$^5$,
- Rico Fischer$^3$,
- Samuel M. Fischer$^3$,
- Jessica Hetzer$^2$,
- Thomas Hickler$^2$,
- Christian	Hochauer$^6$,
- Manfred J. Lexer$^6$,
- Heike	Lischke$^7$,
- Mats Mahnken$^8$,
- Paola	Mairota$^9$,
- Ján Merganič$^{10}$,
- Katarina Merganičová$^{11,12}$,
- Tobias Mette$^{13}$,
- Marco Mina$^{14}$,
- Xavier Morin$^{15}$
- Werner Rammer$^4$,
- Christopher P.O. Reyer$^8$,
- Simon	Scheiter$^2$,
- Daniel Scherrer$^{16}$,
- Harald Bugmann$^1$
date: $^*$Corresponding author (olalla.diaz@usys.ethz.ch) \newline
      $^1$ETH Zurich. Department of Environmental Systems Science. Institute of Terrestrial Ecosystems. Universitätstrasse 16, 8092 Zürich, Switzerland. \newline
      $^2$Senckenberg Biodiversity and Climate Research Centre (SBiK-F), 60325 Frankfurt am Main, Germany. \newline
      $^3$Department of Computational Hydrosystem, Helmholtz-Centre for Environmental Research - UFZ, Permoserstraße 15, 04318 Leipzig, Germany. \newline
      $^4$Ecosystem Dynamics and Forest Management Group, TUM School of Life Sciences, Technical University of Munich, 85354 Freising, Germany. \newline
       $^5$Department of Geoecology, Institute of Botany of the Czech Academy of Sciences, Průhonice, Czech Republic. \newline
       $^6$Institute of Silviculture, Department of Forest and Soil Sciences, University of Natural Resources and Life Sciences, Peter Jordan Strasse 82, A-1190 Vienna, Austria \newline
       $^7$Dynamic Macroecology, Swiss Federal Institute for Forest, Snow and Landscape Research WSL, Zürcherstrasse 111, 8903 Birmensdorf, Switzerland. \newline
       $^8$Potsdam Institute for Climate Impact Research (PIK), Member of the Leibniz Association, 14473 Potsdam, Germany. \newline
       $^9$Department of Soil Sciences, of Plants and Food, University of Bari Aldo Moro, Italy. \newline
       $^{10}$Department of Forest Harvesting, Logistics and Ameliorations, Faculty of Forestry, Technical University in Zvolen \newline
       $^{11}$Czech University of Life Sciences Prague, Faculty of Forestry and Wood Sciences, Kamýcká 129, 16500 Praha 6 – Suchdol, Czech Republic. \newline
       $^{12}$Department of Biodiversity of Ecosystems and Landscape, Slovak Academy of Sciences, Štefánikova 3, P.O.Box 25, 81499 Bratislava, Slovakia. \newline 
       $^{13}$Dpt. of Soil and Climate, Bavarian State Institute of Forestry. \newline 
       $^{14}$Institute for Alpine Environment, Eurac Research, Bolzano/Bozen, Italy. \newline 
       $^{15}$CEFE, CNRS Campus du CNRS 1919, route de Mende 34293 Montpellier cedex, France. \newline 
       $^{16}$Swiss Federal Institute for Forest, Snow and Landscape Research WSL, Zürcherstrasse 111, 8903 Birmensdorf, Switzerland
    \newline  
    \newline
    \today 
output:
  bookdown::pdf_document2:
    keep_tex: yes
    number_sections: yes
    toc: no
    extra_dependencies: "subfig"
  word_document:
    reference_docx: template_paper.docx
mainfont: Arial
fontsize: 12pt
linestretch: 1.5
bibliography: Regeneration.bib
link-citations: yes
nocite: |
  @bugmann1996a, @bohn2014, @fabrika2005, @mette2014, @smith2001a, @langan2017, @seidl2012a, @lischke2006, @schumacher2006, @scheiter2009, @scheller2007, @morin2021, @lasch-born2020, @hickler2012, @fischer_lessons_2016, @langan2017, @scheiter2013 
linkcolor: blue
csl: global-change-biology.csl
editor_options:
  markdown:
    wrap: 72
header-includes:
- \usepackage[left]{lineno}
- \linenumbers
- \usepackage{caption}
- \captionsetup[figure]{font=scriptsize}
- \captionsetup[table]{font=scriptsize}
- \usepackage{titling}
- \predate{\begin{flushleft}}
- \postdate{\end{flushleft}}
---
